Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?

### 2017-01-24 cloneoverflow-latex/cloneoverflow.tex
Updated throughout the paper (again)

\title{Are We Reusing Outdated Code from Stack Overflow?}

@@

Code cloning can also have side effects of violating software licenses and software vulnerabilities. Carelessly cloning code from one project to another project with different license may cause software licensing violation \cite{German2009}. This also happens within the context of online Q\&A website such as Stack Overflow. An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow have potential of violating software licenses. Security is also among the main concerns when code is copied from online source. A study by Acar et al.~shows that Stack Overflow helps developers to solve Android programming problems more quickly than other resources. However, it gives less secure code than books and the official Android documentation \cite{Acar2016}.

@@

In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones. We call them \textbf{online code clones} (or sometimes only call \textbf{clones} for brevity). There are four ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium; and (4) code is cloned from an external source to both a software project and Stack Overflow. Online code clones can similarly lead to a problem of bug propagation, licensing violation, and software vulnerability as classical code clones. Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #22315734 */                    /* WritableComparator.java (2016-09-26) */
public int compare (byte[] b1,int s1,int l1,              public int compare(byte[] b1,int s1,int l1,
                    byte[] b2,int s2,int l2) {                               byte[] b2,int s2,int l2) {
  try {                                                     try {
    buffer.reset(b1,s1,l1); /* parse key1 */                  buffer.reset(b1,s1,l1); /* parse key1 */
    key1.readFields(buffer);                                  key1.readFields(buffer);
    buffer.reset(b2,s2,l2); /* parse key2 */                  buffer.reset(b2,s2,l2); /* parse key2 */
    key2.readFields(buffer);                                  key2.readFields(buffer);
  } catch (IOException e) {                                   buffer.reset(null,0,0); /* clean up reference */
    throw new RuntimeException(e);                          } catch (IOException e) {
  }                                                           throw new RuntimeException(e);
  return compare(key1,key2); /* compare them */             }
}                                                           return compare(key1, key2); /* compare them */
	                                                        }
	\end{lstlisting}
	\caption{The same code fragments, WritableComparator.java, on Stack Overflow post 22315734 and latest version in hadoop code base}
	\label{fig:before-after}
\end{figure*}

A motivating example of problems caused by online code clones can be found in the Stack Overflow post regarding how to implement \textit{RawComparator} in Hadoop\footnote{http://stackoverflow.com/questions/22262310}. In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question. The snippet shows how Hadoop implements \textit{compare} method in its \textit{WritableComparator} class. The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of Hadoop. We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, is added in the latest version after \verb|key2.readFields(buffer);|. The added line is intended for cleaning up the reference in \verb|buffer| variable. While this change has already been introduced into \textit{compare} method in the latest version of Hadoop, the code example in Stack Overflow post is still unchanged and outdated. This example shows that there can be inconsistencies between online code clones and its original resulting in outdated code on Stack Overflow.  %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases. 
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

This paper makes the following  primary contributions:

@@

\section{Empirical Study}
We perform an empirical study of online code clones between Stack Overflow and 109 Java open source projects to answer the following research questions: \\ 
\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We would like to quantitatively measure the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem. \newline
%\textbf{RQ2 (flow of online code clones):} \textit{what are the directions that source code is cloned?} If clones between the two locations exist, we would like to observe in which direction the code has been copied. Is it mostly from Stack Overflow to open source projects, or the other way around, or equally both? \newline
\textbf{RQ2 (reasons for creating online code clones):} \textit{Why do online code clones occur?} We categorise online clones into seven categories according to our clone pattern classification scheme. The patterns of online cloning give more insights to why online code clones are created. %so we can differentiate and understand the motivation of cloning. 
%Clones can be copied from open source projects to Stack Overflow as examples, or vice versa. Furthermore, they can be cloned from a third-party location or clones containing boiler-plate code, and code stubs generated by IDE. \newline
\newline
\textbf{RQ3 (effects of online code clones):} \textit{what are the effects from reusing online code clones? can they be harmful to software development?} %Is there observable problems caused by clones between Stack Overflow and open source projects? 
We are interested to investigate the problem of software licensing and reusing outdated code.

@@

\subsection{Experimental Framework}
To answer the three research questions, an experimental framework is designed as depicted in \Cref{fig:exp_framework}. We process two datasets, Stack Overflow and 111 open source projects from Qualitas corpus. Java code fragments are extracted from Stack Overflow posts using regular expressions. We prepare Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection. Then, we deploy two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to scalability of Simian and NiCad, we partition the input and run the tools multiple times. Each run is composed of the whole Stack Overflow data and single Qualitas project. We repeat the process until we cover 111 projects.

@@

\subsubsection{Prioritise Clone Candidates Using Agreement}
A number of clones detected in large-scale datasets can be huge. In our study, there are totally 266,837,480 clone pairs reported. It is almost infeasible for human to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking at most of the false clones. Therefore, we adopted an idea of \textbf{clone agreement} which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}. By using this agreement-based approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs report by two different tools, we use clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair with a confident value between 0 and 1. A good-match clone pair has stronger agreement than an ok-match pair. We follow the following definitions of good- and ok-match introduced in the original paper.

@@

Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{good-match(p)} iff, for $p \in [0,1]$ holds 
%\squeezeup
\begin{equation}
good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
\end{equation}

@@

Using this good-match and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266-million candidate clone pairs for manual investigation. good-match pairs are the ones with the highest confident and ranked the first to be looked at, followed by ok-match pairs, and followed by clone pairs without agreement.

@@

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) found after filtering by clone agreement and \texttt{equals()}}
	\label{tab:online_clone_pairs}
	\small
	\begin{tabular}{l|r|r|r}
		\hline
		Clone set & C$_{\textrm{\textit{pairs}}}$ & \texttt{equals()} & Manual \\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  & 9 & 2,252 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}    & 26,838 & 9,122 & 200 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}        & 29,099 \\
		\multirow{1}{*}{$S_D$}       & 17,801 & 16,930 & 871 \\
		\multirow{1}{*}{$N_D$}       & 168 & 41 & 127 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total                                               & 47,068 & 26,102 & 3,450 \\ 
		\hline
	\end{tabular} 
\end{table}

@@

As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of agreed clone pairs using good-match is reduced to 2,261 while ok-match is reduced to 26,838. The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 168 for Simian and NiCad respectively. The details are as follows.

\begin{table}
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
		\hline
		\textit{Successful} & 111 & 111 & 105 & 84 \\ 
		\textit{Clustering fail} & -- & -- & 6 & 16 \\
		\textit{Renaming fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.  Similar to the original study, we select a threshold \textit{p} of 0.7 for both good and ok-match \cite{Bellon2007}. The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. We found that NiCad generates errors and stopped processing against some Qualitas projects. \FIXME{Report the errors to NiCad creator.}  $N_D$ could not detect clones in 6 projects due to clustering errors. $N_E$ generated renaming errors for 11 projects, and clustering errors for 16 projects. Hence, we did not have NiCad clones in the agreed clone pairs for these 6 ($N_D$) and 27 projects ($N_E$). This makes Simian clones of the same projects to be removed from the agreed clone pairs as well since they could not have matching online clone pairs.

The distributions of good-match clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}. There are 2,274 good-match pairs (2,261 uniquely) consisting of 10 pairs from$S_DN_D$, 26 pairs from$S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$. According to the definition, ok-match clone pairs always subsume the good-match pairs. There are 26,838 ok-match clone pairs (excluding the 2,261 good-match pairs). 9,052 pairs are from $S_DN_D$, 991 pairs are from $S_DN_E$, 78 are pairs from $S_EN_D$, and 17,549 pairs are from $S_EN_E$. Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations. If we remove duplicates, the number of unique ok-match pairs is 26,838.

%\FIXME{Maybe no longer needed?} We are interested in discovering reused code in the latest versions of Qualitas projects. So, we downloaded the newest release of each project and found 44 of them having newer updates. Then, we reran the experiment again on these 44 projects. Several projects triggered NiCad problem of clustering and renaming again as listed in Table \{tab:projects_missing}. The agreed clone pairs using Bellon's good-match(0.7) and ok-match(0.7) criteria of this new dataset are also listed in Table \{t_agreed_good_clone_pairs}.

\begin{table}[H]
	\centering
	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{D} and \textit{E} settings}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|r|r}
		\hline
		\multirow{2}{*}{Setting} & \multicolumn{2}{c}{No.~of clone pairs}   \\ \cline{2-3}
		& good-match & ok-match \\
		\hline
		$S_DN_D$  & 10 & 9,052    \\ 
		$S_DN_E$  & 26 & 991     \\ 
		$S_EN_D$  & 10 & 78       \\
		$S_EN_E$  & 2,228 & 17,549   \\ 
		\hline
		Total & 2,274 & 27,670   \\
		\hline
		Unique & 2,261 & 26,838  \\
		\hline
	\end{tabular}
\end{table}

\begin{figure*}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3}
		\caption{Distributions of good-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3}
		\caption{Distributions of ok-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with another tool. The disagreement can be from misalignment of clone lines or different configurations that result in different clones reported. They are also clone pairs in projects with NiCad's errors (6 projects for \textit{df} and 27 for \textit{EvCl} configurations) that are missing from the agreed clone pairs. With the four configuration combinations, we decided to investigate only two,$S_D$, and $N_D$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively). They also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.

Even choosing only the default configurations, the number of clone pair candidates are still very large. We hence apply two pruning filters: clone size, and similarity threshold. For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}. The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines). The second filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration. %We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%. %Using the filter along with regular expressions to capture boiler-plate code clones such as \verb|equals()| and \verb|hashcode()|, we can reduce the number of Simian clone candidates to a manageable amount of 795 clone pairs.

% It results in 159 clone pairs remaining. The summary of disagreed clone pairs before and after filtering is shown in \Cref{tab:classification_indv_stats}.
% 9,383 (part 1) + 9,042 (part 2) + 1,923 (part 3) = 20,348 %
For $S_D$, there are 20,348 clone pairs after using 10--line filter. Out of 20,348 pairs, 2,546 of them are ok-match pairs which are discarded. We filtered the results further by removing false positives such as similar \verb|hashCode()| methods, getters and setters out by using regular expressions. We managed to reduce the number to 871 clone pairs remaining for manual investigation. 
% 7062 + 22187 + 6755 =  36004 %
For $N_D$, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well. We thus filter NiCad's clones by using similarity threshold. We increase NiCad's similarity threshold from 70\% to 80\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.2) and obtain 618 clone pairs. %However, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well. So . Using 80\% similarity, there are totally 166 pairs left. 
There are 450 ok-match pairs which we ignore, thus 168 clone pairs remaining for manual investigation. The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.

@@

This is an important question underpinning the motivation of online code cloning. Why are they created and how? Due to an absence of clone oracle of the two data sets, we resort to manual investigation to validate the clone pair candidates as either true or false positives. At the same time, we select a reason that stimulates a creation of each online clone pair. %We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand.

@@

\textbf{Agreed clone pairs}: the classification results are shown in \Cref{tab:classification_good_o}. We have manually investigated 2,261 good-match clone pairs. There is one clone pair in category A which is found to be copied from a Qualitas project to Stack Overflow. Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as category B. We found 3 pairs in category C that are copied from external sources. The rest are false positive clones. 58 clone pairs are found to be \verb|equals()| methods, or getters and setters, category D. Six pairs are similar code from inheritance of the same superclass or implementing the same interface, category E. Finally, 2,189 clone pairs are categorised to E which means they are false clones.

>>>>

\title{Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?}

@@

Code cloning can also have side effects of violating software licenses and software vulnerabilities. Carelessly cloning code from one project to another project with different license may cause software licensing violation \cite{German2009}. This also happens within the context of online Q\&A website such as Stack Overflow. An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow have potential of violating software licenses. Security is also among the main concerns when code is copied from online source. Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, gives less secure code than books and the official Android documentation \cite{Acar2016}. Additionally, outdated and vulnerable third-party libraries from famous open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.

@@

In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones. We call them \textbf{online code clones} (or sometimes only call \textbf{clones} for brevity). There are four ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium; and (4) code is cloned from an external source to both a software project and Stack Overflow. \textbf{Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones.} Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #22315734 */                    /* WritableComparator.java (2016-09-26) */
public int compare (byte[] b1,int s1,int l1,              public int compare(byte[] b1,int s1,int l1,
                    byte[] b2,int s2,int l2) {                               byte[] b2,int s2,int l2) {
  try {                                                     try {
    buffer.reset(b1,s1,l1); /* parse key1 */                  buffer.reset(b1,s1,l1); /* parse key1 */
    key1.readFields(buffer);                                  key1.readFields(buffer);
    buffer.reset(b2,s2,l2); /* parse key2 */                  buffer.reset(b2,s2,l2); /* parse key2 */
    key2.readFields(buffer);                                  key2.readFields(buffer);
  } catch (IOException e) {                                   buffer.reset(null,0,0); /* clean up reference */
    throw new RuntimeException(e);                          } catch (IOException e) {
  }                                                           throw new RuntimeException(e);
  return compare(key1,key2); /* compare them */             }
}                                                           return compare(key1, key2); /* compare them */
	                                                        }
	\end{lstlisting}
	\caption{A motivating example of the same code fragments, WritableComparator.java. The one on Stack Overflow post 22315734 is outdated when compared to its latest version in Hadoop code base}
	\label{fig:before-after}
\end{figure*}

A motivating example of outdated code in online code clones can be found in the a Stack Overflow post regarding how to implement \textit{RawComparator} in Hadoop\footnote{http://stackoverflow.com/questions/22262310}. In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question. The snippet shows how Hadoop implements \textit{compare} method in its \textit{WritableComparator} class. The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of Hadoop. We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, is added in the latest version after \verb|key2.readFields(buffer);|. The added line is intended for cleaning up the reference in \verb|buffer| variable. While this change has already been introduced into \textit{compare} method in the latest version of Hadoop, the code example in Stack Overflow post is still unchanged. This example shows that there can be inconsistencies between online code clones and its original. The code snippet on Stack Overflow can be outdated.  %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases. 
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

While a lot of research has focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and whether these example snippets are still up-to-date.

To fill this gap, this paper makes the following  primary contributions:

@@

\section{Empirical Study}
We perform an empirical study of online code clones between Stack Overflow and 109 Java open source projects to answer the following research questions: \\ 
\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We would like to quantitatively measure the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem. \newline
%\textbf{RQ2 (flow of online code clones):} \textit{what are the directions that source code is cloned?} If clones between the two locations exist, we would like to observe in which direction the code has been copied. Is it mostly from Stack Overflow to open source projects, or the other way around, or equally both? \newline
\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online code clones occur?} We categorise online clones into seven categories according to our online code cloning pattern scheme. This gives us more insights to why online code clones are created. %so we can differentiate and understand the motivation of cloning. 
%Clones can be copied from open source projects to Stack Overflow as examples, or vice versa. Furthermore, they can be cloned from a third-party location or clones containing boiler-plate code, and code stubs generated by IDE. \newline
\newline
\textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We are interested in the correctness of Stack Overflow code examples since millions of users are potentially reusing them.  %Is there observable problems caused by clones between Stack Overflow and open source projects? 
%We are interested to investigate the problem of outdated code and software licensing conflicts caused by online code clones.

\textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We would like to investigate whether online code clones can be legally harmful to software reusing them.

@@

\subsection{Experimental Framework}
To answer the four research questions, an experimental framework is designed as depicted in \Cref{fig:exp_framework}. We process two datasets, Stack Overflow and 111 open source projects from Qualitas corpus. Java code fragments are extracted from Stack Overflow posts using regular expressions. We prepare Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection. Then, we deploy two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to scalability of Simian and NiCad, we partition the input and run the tools multiple times. Each run is composed of the whole Stack Overflow data and single Qualitas project. We repeat the process until we cover 111 projects.

@@

\subsubsection{Prioritise Clone Candidates Using Agreement}
A number of clones detected in large-scale datasets can be huge. In our study, there are totally 266,837,480 clone pairs reported. It is almost infeasible for human to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking at most of the false clones. Therefore, we adopted an idea of \textbf{clone agreement} which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}. By using this agreement-based approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs report by two different tools, we use clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1. A \textit{good} clone pair has stronger agreement than an \textit{ok} pair. We follow the following definitions of good- and ok-match introduced in the original paper.

@@

Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(p)} iff, for $p \in [0,1]$ holds 
%\squeezeup
\begin{equation}
good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
\end{equation}

@@

Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266-million candidate clone pairs for manual investigation. \textit{good} pairs are the ones with the highest confident and ranked the first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.

@@

\begin{table*}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering. The last column shows the number of true positive clone pairs after the manual investigation.}
	\label{tab:online_clone_pairs}
	\small
	\begin{tabular}{l|r|l|r|r|r|r}
		\hline
		Clone set & Original & Filter & Candidates & \texttt{equals()} & Manual & TP \\ 
		\hline 
		\multirow{1}{*}{\textit{good}} & --  & -- & 2,261  & 9 & 2,252 & 8 \\
		\multirow{1}{*}{\textit{ok}} & --  & -- & 26,838 & 9,122 & 200 & 47 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}        & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & $Line \geq 10$, RegEx, good/ok & 17,801 & 16,930 & 871 & 432 \\
		\multirow{1}{*}{$N_D$} & 229,176 & $Sim \geq 80\%$, RegEx, good/ok & 168 & 41 & 127 & 36 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 296,746 & & 47,068 & 26,102 & 3,450 & 523 \\ 
		\hline
	\end{tabular} 
\end{table*}

@@

As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} agreed clone pairs is 2,261 while \textit{ok} is 26,838. The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 168 for Simian and NiCad respectively. The details are as follows.

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.  Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. We found that NiCad generates errors and stopped processing against some Qualitas projects. \FIXME{Reported the errors to NiCad creator. Add response here.}  $N_D$ could not detect clones in 6 projects due to clustering errors. $N_E$ generated renaming and clustering errors for 11 and 16 projects respectively. As a result, we did not have NiCad clones from these project in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

\begin{table}
	\centering
	\caption{No.~of successfully analysed Qualitas projects}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
		\hline
		\textit{Successful} & 111 & 111 & 105 & 84 \\ 
		\textit{Clustering fail} & -- & -- & 6 & 16 \\
		\textit{Renaming fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}

\begin{table}
	\centering
	\caption{Distribution of agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r}
		\hline
		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Total & Unique \\
		\hline
		\textit{good} & 10 & 26 & 10 & 2,228 & 2,274 & 2,261 \\
		\textit{ok} & 9,052 & 991 & 78 & 17,549 & 27,670 & 26,838 \\
		\hline
	\end{tabular} %
}
\end{table}

The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}. There are 2,261 unique \textit{good} pairs consisting of 10 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$. There are 26,838 unique \textit{ok} pairs (excluding the subsumed 2,261 \textit{good} pairs).\footnote{According to the definition, \textit{ok} clone pairs always subsume the \textit{good} pairs.} We obtained 9,052; 991; 78; and 17,549 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively. Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:venn4_orig_ok}), but there is no clone pair that is agreed by all four combinations. %If we remove duplicates, the number of unique ok-match pairs is 26,838.

%\FIXME{Maybe no longer needed?} We are interested in discovering reused code in the latest versions of Qualitas projects. So, we downloaded the newest release of each project and found 44 of them having newer updates. Then, we reran the experiment again on these 44 projects. Several projects triggered NiCad problem of clustering and renaming again as listed in Table \{tab:projects_missing}. The agreed clone pairs using Bellon's \textit{good}(0.7) and ok-match(0.7) criteria of this new dataset are also listed in Table \{t_agreed_good_clone_pairs}.

\begin{figure*}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3}
		\caption{Distributions of \textit{good} pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3}
		\caption{Distributions of \textit{ok} pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

The disagreed clone pairs are clone pairs that are reported by a tool, either Simian or NiCad, and do not have agreement with clones from another tool. The disagreement can be from misalignment of clone lines or different configurations that result in dissimilar clones reported. They also cover clone pairs in projects having NiCad's errors (6 projects for $N_D$ and 27 for $N_E$) that are automatically missing from the agreed clone pairs. With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and drop $S_E$ and $N_E$ due to their enormous amount of clone pairs (59 and 206 millions respectively). $S_E$ and $N_E$ also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.

Even choosing only the default configurations, the number of clone pair candidates are still very large. We hence apply three filters: \textbf{clone size, regular expression, and similarity threshold}. For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}. The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods, getters and setters using regular expressions and removes them. The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration. %We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%. %Using the filter along with regular expressions to capture boiler-plate code clones such as \verb|equals()| and \verb|hashcode()|, we can reduce the number of Simian clone candidates to a manageable amount of 795 clone pairs.

% It results in 159 clone pairs remaining. The summary of disagreed clone pairs before and after filtering is shown in \Cref{tab:classification_indv_stats}.
% 9,383 (part 1) + 9,042 (part 2) + 1,923 (part 3) = 20,348 %
As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size and regular expressions. The combination of the two filters reduce the number of $S_D$ clones to 17,801 pairs for manual investigation. 
% 7062 + 22187 + 6755 =  36004 %
For $N_D$, 10-line threshold is already a minimum NiCad's clone size. However, NiCad still reported much more clones than Simian since it can detect type-3 clones. Thus, we filtered NiCad's clones by using similarity threshold and regular expressions. We increase NiCad's similarity threshold from 70\% to 80\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.2). We have tried varying the UPI from 70\%, 80\% and 90\% and we found that 80\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation. Using the two filters, we reduced the size of $N_D$ clones to 168 pairs.

%However, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well. So . Using 80\% similarity, there are totally 166 pairs left. 
%There are 450 ok-match pairs which we ignore, thus 168 clone pairs remaining for manual investigation. %The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.

In our manual investigation process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 26,102 pairs out of 47,068 (more than half of the \texttt{equals()} pairs came from $S_D$). Finally, there are 3,450 pairs remaining which we manually investigated them. \textbf{To answer RQ1, we found 47,068 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. After a manual investigation, we found at least 523 online code clones pairs are true clones.}

@@

Besides the quantitative analysis, we are also interested in a qualitative analysis of the online clones. Why are they created and how? Due to an absence of clone oracle of the two data sets, we resort to manual investigation to validate the clone pair candidates as either true or false positives. At the same time, we select a reason that stimulates a creation of each online clone pair. %We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand.

@@

\textbf{Agreed clone pairs}: the classification results are shown in \Cref{tab:classification_good_o}. We have manually investigated 2,261 \textit{good} clone pairs. There is one clone pair in pattern A which is found to be copied from a Qualitas project to Stack Overflow. Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as pattern B. We observed 3 pairs in pattern C since they are copied from external sources. %The rest are boilter-plate, inherit/interface, and false positive clones. 
58 clone pairs are found to be pattern D: \verb|equals()| methods, or getters and setters. Six pairs are similar code from inheriting the same superclass or implementing the same interface, pattern E. Finally, 2,189 clone pairs are categorised to F which means they are false clones.
